Title

### 2019-05-03 4_method.tex
make legend

@@

\paragraph{point-point segments}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + \frac12 d}$.
The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{x}{\sqrt{x^2 + d/2}}$
So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
%Wolfram Alpha:
so $\abs x < \frac{\sqrt{d}}{\sqrt{6}} \approx 0.408 d$.
So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}

>>>>

For an explanation of the terms used, see \cref{legend}.

\begin{figure}
\includegraphics[width=\columnwidth]{sources/method/legend_double_wedge_example.pdf}
\caption{Explanation of terms.}
\label{legend}
\end{figure}

@@

\paragraph{point-point segments}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the MAT segment is given by $y=\frac12 d$.
For a given $x$ the distance $D$ to the outline vertices is given by $D = \sqrt{x^2 + (\frac12 d)^2}$.
The ratio between MAT distance $D$ and Euclidean distance $\abs x$ is determined by $\frac{\partial D}{\partial x} / \frac{\partial \abs x}{x} = \abs \frac{2x}{ \sqrt{4x^2 + d^2}}$
So the Euclidean distance is more than twice the MAT distance then $\abs \frac{\partial D}{\partial x}  < \frac12$, 
%Wolfram Alpha:
so $\abs x < \frac{d}{2\sqrt{3}} \approx 0.289 d$.
So we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-\frac{\sqrt{d}}{\sqrt{6}}, \frac{\sqrt{d}}{\sqrt{6}}]$.
\hl{But that is very weird in combination with the rule that the ends of marked segments should always be rounded! Isn't it?!}
